---
title: "Marketing Report"
subtitle: "Office of Marketing and Brand Management"
date: "`r Sys.Date()`"

output:
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
  tufte::tufte_html: default
  tufte::tufte_book:
    citation_package: natbib
    latex_engine: tinytex
bibliography: skeleton.bib
link-citations: yes
---

```{r setup, include=FALSE}
library(tufte)
library(knitr)
library(formatR)
library(blastula)
library(gt)
library(glue)
library(formattable)
library(hms)
library(tidyverse)
library(knitr)
library(ggpubr)
library(salesforcer)
library(knitr)
library(RForcecom)


# invalidate cache when the tufte version changes
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	cache.extra = packageVersion("tufte"),
	tidy = FALSE
)
options(tinytex.verbose = TRUE)
```

```{r, include=FALSE}
options(tinytex.verbose = TRUE)
```

# __FY21 Analytics Project Template__

# Description


`r newthought('Intro text here')` Intro text here Intro text here Intro text here Intro text here Intro text here Intro text here Intro text here Intro text here. In general,
    \href{https://blog.adstage.io/facebook-ads-benchmarks}{{\color{blue}{\underline{FB Newsfeed }}}} CTR overall experienced a 24% drop from July, 2017 - July, 2018.




# Findings


__Margin Figures__




```{r eval=FALSE, include=FALSE}
imgur_image <-
   add_imgur_image(
     image = a_a,
     client_id = "851117406f0b457"
   )

```


```{r}
username <- "christine.iyer@maine.edu"
password <- "1Edithandoliver"
securityToken <- "iFhpXgaXnuP3L5PQr69Zw2yOy"
instanceURL <- "https://login.salesforce.com/"
apiVersion <- "44.0"

#auth <- sf_auth(username = username, password = password, security_token = securityToken,
#login_url = getOption("https://login.salesforce.com/"))



session <- sf_auth(username, password, securityToken, instanceURL, apiVersion)
username <- "christine.iyer@maine.edu"
password <- "1EdithandoliveriFhpXgaXnuP3L5PQr69Zw2yOy"
#securityToken <- ""
instanceURL <- "https://na24.salesforce.com/"
apiVersion <- "44.0"


session <- rforcecom.login(username, password, instanceURL,apiVersion  ) 



```


## __FY21 Senior Leads Purchased who have Converted to Inqs or Apps__

```{r}
my_soql1 <- sprintf("SELECT Id,
                           CreatedDate,
                           Email, 
                           FirstName, 
                           LastName,
                           TargetX_SRMb__Status__c, TargetX_SRMb__Student_Type__c,
                           TargetX_SRMb__Anticipated_Start_Term__c,
                           TargetX_SRMb__Anticipated_Start_Term_Year__c, 
                           TargetX_SRMb__Anticipated_Start_Year__c,
                           App_Application_Date__c,  
                           TargetX_SRMb__Gender__c,  
                           TargetX_SRMb__Last_Data_Input_Source__c,                                                                                                        Initial_Source_Date__c, 
                           Initial_Referral_Source__c, 
                           Recruiting_Category__c,
                           Ref__c, 
                           Primary_State_Code__c, 
                           Lead_Segment_College_Board__c, 
                           Lead_Segment_NRCCUA__c, 
                           Lead_Segment_Niche__c, 
                           Lead_Segment_Cappex__c
                           
                           
                    FROM Contact 
                    WHERE (
                    (DAY_ONLY(CreatedDate) > 2020-07-01 
                    AND DAY_ONLY(CreatedDate) < 2020-10-21
                    AND (Lead_Segment_Cappex__c != Null
                    OR Lead_Segment_Niche__c != Null)
                    AND TargetX_SRMb__Anticipated_Start_Term_Year__c = 'Fall 2021'
                    AND TargetX_SRMb__Status__c != 'Lead')
                    
                    OR (DAY_ONLY(CreatedDate) > 2020-10-16 
                    AND DAY_ONLY(CreatedDate) < 2020-10-21
                    AND (Lead_Segment_College_Board__c != Null
                    OR Lead_Segment_NRCCUA__c  != Null)
                    AND TargetX_SRMb__Anticipated_Start_Term_Year__c = 'Fall 2021'
                    AND TargetX_SRMb__Status__c != 'Lead')
                    )
                    ")

queried_records1 <- sf_query(my_soql1)

kable(queried_records1 %>% select(Id, TargetX_SRMb__Status__c))
```



```{r}
write.csv(queried_records1, file = paste0("C:/Users/christine.iyer/Box/FY21 Search/Search 1/Data Tidying/FY21_SF_Queried_Inq_and_Apps/FY21_October_SR_", Sys.Date(), "_.csv"), row.names = F)
```





# Conclusions

 
* 
* 


\href{https://www.wrike.com/open.htm?id=570713380}{{\color{blue}{\underline{Wrike Project Details}}}}

\href{https://github.com/edithbird/FY21_Search_Name_Purchase}{{\color{blue}{\underline{Github Repository}}}}

